Predicting trends in the quality of state-of-the-art neural networks without access to training or testing data

### 2021-01-09 submission/NatCom_appendix.tex
appendix updated

In our github repository, we provide several python Juoyter Google Colab anotebooks,
as well as previously generated data,  which can be used to reproduce the results of Section~\ref{sxn:all_cv_models}, 
and using the \texttt{WeightWatcher} tool (version 0.2.7), as described in Table~\ref{table:notebooks}.
The ImageNet-1K and other pretrained models are taken from the pyTorch models in the \texttt{omsr/imgclsmob} 
``Sandbox for training convolutional networks for computer vision'' github repository~\cite{osmr}.
The full  \texttt{WeightWatcher} results are provided in the datasets: \texttt{[data/osmr/data...xlsx]},
last generated in January 2020, using the Google Colab notebooks: \texttt{[ww\_colab/ww\_colab...ipynb]}.
These data files are analyzed with the \texttt{OSMR-Analysis.ipynb} python Juyter Notebook,
which runs all regressions and which tabulates the results presented in Table~\ref{table:results}
and generates the figures in Figures~\ref{fig:summary_regressions_A}-\ref{fig:summary_regressions_I}.

We attempt to run linear regressions for all pyTorch models for each architecture series for all datasets provided.  
There are over $450$ models in all, and we note that the \texttt{osmr/imgclsmob} repository is constantly being updated with new models.
We omit the results for CUB-200-2011, Pascal-VOC2012, ADE20K, and COCO datasets, as there are fewer than 15 models for those datasets.  
Also, we filter out regressions with fewer than 5 datapoints.

@@

See
Figure~\ref{fig:summary_regressions_A},
Figure~\ref{fig:summary_regressions_B},
Figure~\ref{fig:summary_regressions_C},
Figure~\ref{fig:summary_regressions_D},
Figure~\ref{fig:summary_regressions_E},
Figure~\ref{fig:summary_regressions_F},
Figure~\ref{fig:summary_regressions_G},
Figure~\ref{fig:summary_regressions_H}, and
Figure~\ref{fig:summary_regressions_I} for more details.
\michael{Charles, would you put a bit of discussion, e.g., on best and worst, again just a teaser to satisfy that reviewer.}
\charles{below}
From these Figures, we recognize fits of varying quality, ranging from remarkably good to completely uncorrelated.
Starting with the best, consider the Imagenet-1K PreResNet results.  Figure~\ref{fig:summary_regressions_A_10} shows 
the Avg. Log Spectral Norm $\langle\log\Vert\mathbf{W}\Vert^{2}_{\infty}\rangle$, 
which has a rather large $RMSE=3.93$, and rather small $R2=0.36$, and Kendal-$\tau=0.54$, and
has 6 out of 13 points outside the $95\%$ confidence bands.  In contrast, 
the Avg. Log Alpha Norm $\langle\log\Vert\mathbf{W}\Vert^{\alpha}_{\alpha}\rangle$, 
in  Figure~\ref{fig:summary_regressions_A_12} , 
has a much smaller $RMSE=1.93$, and much larger  $R2=0.85$, and Kendal-$\tau=0.87$, 
and only 2 points outside the $95\%$ confidence bands.
For examples of lower quality fits, consider the SqueezeNext results, as shown Figures~\ref{fig:summary_regressions_C_10} and 
~\ref{fig:summary_regressions_C_12}.  
The Avg. Log Spectral Norm $\langle\log\Vert\mathbf{W}\Vert^{2}_{\infty}\rangle$,
is visually anti-correlated  with the test accuracies
(as it is with ShuffleNet, in Figure ~\ref{fig:summary_regressions_B_02}).
with a very large $95\%$ confidence band, with only 2 points close to the regression line,
a large RMSE,  $R2=0.07$ (i.e zero), and small Kendal-$\tau=0.33$.
The Avg. Log Alpha Norm $\langle\log\Vert\mathbf{W}\Vert^{\alpha}_{\alpha}\rangle$ is always positively-correlated
with test accuracies, but with $R2=43$, which is not great--but not zero, and a reasonable Kendal-$\tau=0.73$.

>>>>

The reader may regenerat all of the  results of Section~\ref{sxn:all_cv_models} 
\texttt{WeightWatcher} results using the Google Colab Jupyter notebooks (in the \texttt{ww-colab} folder)
and  the \texttt{WeightWatcher} tool, 
and/or simply reproduce the Tables and Figures using the Jupyter notebooks (shown in Table~\ref{table:notebooks}),
and the pre-computed \texttt{WeightWatcher} datasets (in the \texttt{data/osmr} folder).
The ImageNet-1K and other pretrained models are taken from the pyTorch models in the \texttt{omsr/imgclsmob} 
``Sandbox for training convolutional networks for computer vision'' github repository~\cite{osmr}.
The full  \texttt{WeightWatcher} results are provided in the datasets: \texttt{[data/osmr/data...xlsx]},
last generated in January 2020, using the Google Colab notebooks: \texttt{[ww\_colab/ww\_colab...ipynb]}.
These data files are analyzed with the \texttt{OSMR-Analysis.ipynb} python Juyter Notebook,
which runs all regressions and which tabulates the results presented in Table~\ref{table:results}
and generates the figures in Figures~\ref{fig:summary_regressions_A}-\ref{fig:summary_regressions_I}.

We attempt to run linear regressions for all pyTorch models for each architecture series for all datasets provided.  
There are over $450$ models in all to consider, and we note that the \texttt{osmr/imgclsmob} repository is constantly being updated with new models.
We omit the results for CUB-200-2011, Pascal-VOC2012, ADE20K, and COCO datasets, as there are fewer than 15 models for those datasets.  
Also, we filter out regressions with fewer than 5 datapoints.

@@

See
Figure~\ref{fig:summary_regressions_A}-\ref{fig:summary_regressions_I} for more details.
%5Figure~\ref{fig:summary_regressions_B},
%Figure~\ref{fig:summary_regressions_C},
%Figure~\ref{fig:summary_regressions_D},
%Figure~\ref{fig:summary_regressions_E},
%Figure~\ref{fig:summary_regressions_F},
%Figure~\ref{fig:summary_regressions_G},
%Figure~\ref{fig:summary_regressions_H}, and

\michael{Charles, would you put a bit of discussion, e.g., on best and worst, again just a teaser to satisfy that reviewer.}
\charles{below}
From these Figures, we recognize fits of varying quality, ranging from remarkably good to completely uncorrelated.
Starting with the best, consider the Imagenet-1K PreResNet results.  Figure~\ref{fig:summary_regressions_A_10} shows 
the Avg. Log Spectral Norm $\langle\log\Vert\mathbf{W}\Vert^{2}_{\infty}\rangle$, 
which has a rather large $RMSE=3.93$, and rather small $R2=0.36$, and Kendal-$\tau=0.54$, and
has 6 out of 13 points outside the $95\%$ confidence bands.  In contrast, 
the Avg. Log Alpha Norm $\langle\log\Vert\mathbf{W}\Vert^{\alpha}_{\alpha}\rangle$, 
in  Figure~\ref{fig:summary_regressions_A_12} , 
has a much smaller $RMSE=1.93$, and much larger  $R2=0.85$, and Kendal-$\tau=0.87$, 
and only 2 points outside the $95\%$ confidence bands.
For examples of lower quality fits, consider the SqueezeNext results, as shown Figures~\ref{fig:summary_regressions_C_10} and 
~\ref{fig:summary_regressions_C_12}.  
The Avg. Log Spectral Norm $\langle\log\Vert\mathbf{W}\Vert^{2}_{\infty}\rangle$,
is visually anti-correlated  with the test accuracies
(as it is with ShuffleNet, in Figure ~\ref{fig:summary_regressions_B_02}).
with a very large $95\%$ confidence band, with only 2 points close to the regression line,
a large RMSE,  $R2=0.07$ (i.e zero), and small Kendal-$\tau=0.33$.
The Avg. Log Alpha Norm $\langle\log\Vert\mathbf{W}\Vert^{\alpha}_{\alpha}\rangle$ is (as always) positively-correlated
with test accuracies, but with $R2=43$, which is not great--but not zero, and a reasonable Kendal-$\tau=0.73$.
